Vitis riparia LM

### 2018-11-02 V_riparia_LM.Rmd
V. riparia setup

>>>>

Tooth area:internal perimeter
```{r}
r_taip13_mean <-  riparia %>% 
  filter(year == 2013) %>% 
  group_by(leaf) %>% 
  summarize(avg.taip = mean(tooth.area.int.perimeter, na.rm = TRUE))

r_taip15_mean <- riparia %>% 
  filter(year == 2015) %>% 
  group_by(leaf) %>% 
  summarize(avg.taip = mean(tooth.area.int.perimeter, na.rm = TRUE))
```

Tooth area:blade area
```{r}
r_taba13_mean <-  riparia %>% 
  filter(year == 2013) %>% 
  group_by(leaf) %>% 
  summarize(avg.taba = mean(tooth.area.blade.area, na.rm = TRUE))

r_taba15_mean <- riparia %>% 
  filter(year == 2015) %>% 
  group_by(leaf) %>% 
  summarize(avg.taba = mean(tooth.area.blade.area, na.rm = TRUE))
```

Total teeth:perimeter
```{r}
r_tp13_mean <-  riparia %>% 
  filter(year == 2013) %>% 
  group_by(leaf) %>% 
  summarize(avg.tp = mean(teeth.perimeter, na.rm = TRUE))

r_tp15_mean <- riparia %>% 
  filter(year == 2015) %>% 
  group_by(leaf) %>% 
  summarize(avg.tp = mean(teeth.perimeter, na.rm = TRUE))
```

Total teeth: internal perimeter
```{r}
r_tip13_mean <-  riparia %>% 
  filter(year == 2013) %>% 
  group_by(leaf) %>% 
  summarize(avg.tip = mean(teeth.int.perimeter, na.rm = TRUE))

r_tip15_mean <- riparia %>% 
  filter(year == 2015) %>% 
  group_by(leaf) %>% 
  summarize(avg.tip = mean(teeth.int.perimeter, na.rm = TRUE))
```

Perimeter ratio
```{r}
r_pr13_mean <-  riparia %>% 
  filter(year == 2013) %>% 
  group_by(leaf) %>% 
  summarize(avg.pr = mean(perimeter.ratio, na.rm = TRUE))

r_pr15_mean <- riparia %>% 
  filter(year == 2015) %>% 
  group_by(leaf) %>% 
  summarize(avg.pr = mean(perimeter.ratio, na.rm = TRUE))
```

Compactness
```{r}
r_cp13_mean <-  riparia %>% 
  filter(year == 2013) %>% 
  group_by(leaf) %>% 
  summarize(avg.cp = mean(compactness, na.rm = TRUE))

r_cp15_mean <- riparia %>% 
  filter(year == 2015) %>% 
  group_by(leaf) %>% 
  summarize(avg.cp = mean(compactness, na.rm = TRUE))
```

Shape factor
```{r}
r_sf13_mean <-  riparia %>% 
  filter(year == 2013) %>% 
  group_by(leaf) %>% 
  summarize(avg.sf = mean(shape.factor, na.rm = TRUE))

r_sf15_mean <- riparia %>% 
  filter(year == 2015) %>% 
  group_by(leaf) %>% 
  summarize(avg.sf = mean(shape.factor, na.rm = TRUE))
```

We tested leaf number and total teeth.
```{r}
r_tt_plot <- ggplot(riparia, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
r_tt_plot <- r_tt_plot +labs(x = "Leaf number",
                               y = "Total teeth")
r_tt_plot
```

```{r}
r_tt_mean_plot <- ggplot(r_l_means, aes(x = leaf, y = avg.tt)) + geom_line() + theme_classic()
r_tt_mean_plot <- r_tt_mean_plot +labs(x = "Leaf number",
                               y = "Total teeth")
r_tt_mean_plot
```

We ran a LM for leaf number and total teeth.
```{r}
r_tt_lm <- lm(avg.tt ~ leaf, data = r_l_means)
summary(r_tt_lm)
```

```{r}
r_tt_seg <- segmented(r_tt_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(r_tt_seg)
```

```{r}
r_tt_seg$psi
slope(r_tt_seg)
r_tt_fitted <- fitted(r_tt_seg)
r_tt_model <- data.frame(Leaf = r_l_means$leaf, TT = r_tt_fitted)
ggplot(r_tt_model, aes(x = Leaf, y = TT)) + geom_line()
r_tt_lines <- r_tt_seg$psi[, 2]
r_tt_mean_break <- r_tt_plot + geom_vline(xintercept = r_tt_lines, linetype = "dashed")
r_tt_mean_break
ggsave("r_tt_break.png")
```

We tested leaf number and feret diameter ratio.
```{r}
r_fdr_plot <- ggplot(riparia, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 13, 1))
r_fdr_plot <- r_fdr_plot +labs(x = "Leaf number",
                               y = "FDR")
r_fdr_plot
```

```{r}
r_fdr_mean_plot <- ggplot(r_l_means, aes(x = leaf, y = avg.fdr)) + geom_line() + theme_classic()
r_fdr_mean_plot <- r_fdr_mean_plot +labs(x = "Leaf number",
                               y = "FDR")
r_fdr_mean_plot
```

We ran a LM for leaf number and feret diameter ratio.
```{r}
r_fdr_lm <- lm(avg.fdr ~ leaf, data = r_l_means)
summary(r_fdr_lm)
```

```{r}
r_fdr_seg <- segmented(r_fdr_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(3, 7, 10)))
summary(r_fdr_seg)
```

```{r}
r_fdr_seg$psi
slope(r_fdr_seg)
r_fdr_fitted <- fitted(r_fdr_seg)
r_fdr_model <- data.frame(Leaf = r_l_means$leaf, FDR = r_fdr_fitted)
ggplot(r_fdr_model, aes(x = Leaf, y = FDR)) + geom_line()
r_fdr_lines <- r_fdr_seg$psi[, 2]
r_fdr_mean_break <- r_fdr_plot + geom_vline(xintercept = r_fdr_lines, linetype = "dashed")
r_fdr_mean_break
ggsave("r_fdr_break.png")
```
